The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl

### 2018-02-19 suppinfo.tex
feb 16 (ralph's corrections included)
Ralph's corrections, theoretical figures changed, 1s -> nl replaced by
1s-1 nl

%\begin{figure}
%\centering
%\includegraphics[scale=0.3]{figures/fg2_k_6w_okxx_55_rad_dens.eps}
%\caption{Radial density distributions of the singly-occupied natural orbitals occupied by the excited electron in the core excited states 3609.11\,eV (1\,$^{1}$A$_{2}$), 3609.41\,eV (2\,$^{1}$E) and 3609.64\,eV (3\,$^{1}$E) of K$^{+}$(H$_2$O)$_6$. The grey line at 2.816\,\AA~represents the equilibrium K-O distance.}
%\label{fg:rad_dens}
%\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$\rightarrow$4p, 1s$\rightarrow$3d and 1s$\rightarrow$5p core excitations in \ki~(lower panel) and \cli~(upper panel). The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
\label{fg:si_rdens_ions}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$^{-1}$4p, 1s$^{-1}$3d and 1s$^{-1}$5p core excitations in \ki~(lower panel) and \cli~(upper panel). The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
\label{fg:si_rdens_ions}
\end{figure}
{\color{red}
In what follows we give a tentative explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli. In the case of \ki, the excited electron mainly sees a $2/r$ potential. In addition, it sees a short range potential coming from the pointlike nucleus and the screening electrons. The latter one normally leads to a quantum defect different from 0. Beside this one has Rydberg series with an infinite number of states. However, in case of Cl- the outer electron does not see a Coulomb potential and the short-range potential becomes dominant. As a result we see the unusual behaviour, like e.g. a finite number of bound states (here obviously 4p). In contrast to this 3d and 5p are in the continuum.}
